Minicaml, a purely functional, didactical programming language with an interactive REPL. WORK IN PROGRESS DRAFT

### 2019-12-25 paper/paper.tex
working on paper

\title{Minicaml, a purely functional, didactical programming language with an
interactive REPL.}
\author{Alessandro Cheli\\Course taught by Prof. Gianluigi Ferrari\\and Prof. Francesca Levi}
\begin{document}
\begin{titlingpage}
\maketitle

@@

\section{Tests}
Unit testing is extensively performed using the alcotest testing framework.

>>>>

\title{Minicaml, a purely functional, didactical programming language with an
interactive REPL. WORK IN PROGRESS DRAFT}
\author{Alessandro Cheli\\Course taught by Prof. Gianluigi Ferrari\\and Prof. Francesca Levi}
\begin{document}
\begin{titlingpage}
\maketitle

@@

\section{Tests}
Unit testing is extensively performed using the alcotest testing framework. Code
coverage is provided by the \texttt{bisect\_ppx} library which yields an HTML
page when tests are run by dune.
